### 2023-12-19 documentation/thesis/thesis_document.tex
more thesis
added drawio sources

\begin{itemize}
\tightlist
\item
  usb, ethernet
\item
  pps input output
\item
  multiplexer for i2c sensors alredy implemented
\end{itemize}

@@

\begin{itemize}
\item
  automatic sensor detation ablaufdiagramm erst nach i2c geräte scannen
  dann analog versuchen
\item
  serial cli support for manual mode
\item
  sync impulse =\textgreater{} 1 mastersensor als taktqelle
\item
  interene mittelung und speichern der werte im buffer ringubber welcher
  bei jedem sync impuls neu belegt wird
\item
  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \setcounter{enumi}{1}
  \tightlist
  \item
    core übernimmt mittelung und auswetung
  \end{enumerate}
\item
  was durch den user implementiert werden muss klasse
\end{itemize}

\begin{lstlisting}[language={C++}, caption={CustomSensor-Class for adding new sensor hardware support}, label=lst:CustomSensorClass]
#ifndef __CustomSensor_h__
#define __CustomSensor_h__
// register your custom sensor in implemented_sensors.h also
class CustomSensor: public baseSensor {}
{
public:
    CustomSensor();
    ~CustomSensor();
    // implement depending sensor communication interface
    bool begin(TwoWire& _wire_instance); // I2C
    bool begin(HardwareSerial& _serial_instance); // UART
    bool begin(Pin& _pin_instance); // ANALOG like analog input / DIGITAL PIN like onewire
    // FUNCTIONS USED BY READOUT LOGIC
    bool is_valid() override;
    String capabilities() override;
    String get_sensor_name() override;
    bool query_sensor() override;
    sensor_result get_result() override;        
};
#endif
\end{lstlisting}

@@

\begin{itemize}
\tightlist
\item
  Use with \gls{mrp}-library (see \ref{software-readout-framework})
\item
  Stand-alone mode via sending commands using built-in \gls{cli}
\end{itemize}

@@

\hypertarget{sensor-syncronsisation}{%
\section{Sensor Syncronsisation}\label{sensor-syncronsisation}}

@@

\begin{longtable}[]{@{}llll@{}}
\caption{Build sensors with different capabilities
\label{Build_sensors_with_different_capabilities.csv}}\tabularnewline
\toprule
& 1D (Chapter \ref{d-single-sensor}) & 1D: dual sensor & 3D: fullsphere
(Chapter \ref{d-fullsphere})\tabularnewline
\midrule
\endfirsthead
\toprule
& 1D (Chapter \ref{d-single-sensor}) & 1D: dual sensor & 3D: fullsphere
(Chapter \ref{d-fullsphere})\tabularnewline
\midrule
\endhead
Maximal magnet size & Cubic 30x30x30 & Cubic 30x30x30 & Cubic
20x20x20\tabularnewline
Sensor type & MMC5603NJ & TLV493D & TLV493D\tabularnewline
Sensor count & 1 & 2 & 1\tabularnewline
Scanmode & static (1 point) & static (2 points) & dynamic
(fullsphere)\tabularnewline
\bottomrule
\end{longtable}

@@

As the sensors shown so far relate exclusively to self-built, low-cost
hardware, the following section shows how existing hardware can be
integrated into the system. This is shown here using a
temperature-compensated \passthrough{\lstinline!Voltcraft GM-70!}
telsameter\ref{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board.png},
which has a measuring range of \passthrough{\lstinline!0-3T!} with a
resolution of 0.1mT. This offers an \passthrough{\lstinline!RS232!}
interface with a documented protocol for connection to a \gls{pc}. This
connectivity makes it possible to make the device compatible with the
\gls{mrp} library using interface software \cite{VoltcraftGM70Rest}
executable on the host \gls{pc}. However, it does not offer the range of
functions that the
\passthrough{\lstinline!Unified Sensor Firmware!}\ref{firmware} offers.

@@

>>>>

\begin{itemize}
\tightlist
\item
  usb, ethernet
\item
  pps input output
\item
  multiplexer for i2c sensors alredy implemented
\item
  imput / output for sync
\end{itemize}

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Unified_sensor_firmware_simplified_program_strucutre.png}
\caption{Unified sensor firmware simplified program strucutre
\label{Unified_sensor_firmware_simplified_program_strucutre.png}}
\end{figure}

\begin{itemize}
\item
  mbed
\item
  automatic sensor detation ablaufdiagramm erst nach i2c geräte scannen
  dann analog versuchen
\item
  serial cli support for manual mode
\item
  sync impulse =\textgreater{} 1 mastersensor als taktqelle
\item
  interene mittelung und speichern der werte im buffer ringubber welcher
  bei jedem sync impuls neu belegt wird
\item
  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \setcounter{enumi}{1}
  \tightlist
  \item
    core übernimmt mittelung und auswetung
  \end{enumerate}
\item
  was durch den user implementiert werden muss klasse
\end{itemize}

\ref{Unified_sensor_firmware_simplified_program_strucutre.png}

\ref{lst:CustomSensorClass}

\begin{lstlisting}[language={C++}, caption={CustomSensor-Class for adding new sensor hardware support}, label=lst:CustomSensorClass]
#ifndef __CustomSensor_h__
#define __CustomSensor_h__
// register your custom sensor in implemented_sensors.h also
class CustomSensor: public baseSensor {}
{
public:
    CustomSensor();
    ~CustomSensor();
    // implement depending sensor communication interface
    bool begin(TwoWire& _wire_instance); // I2C
    bool begin(HardwareSerial& _serial_instance); // UART
    bool begin(Pin& _pin_instance); // ANALOG or DIGITAL PIN like onewire
    // FUNCTIONS USED BY READOUT LOGIC
    bool is_valid() override;
    String capabilities() override;
    String get_sensor_name() override;
    bool query_sensor() override;
    sensor_result get_result() override;        
};
#endif
\end{lstlisting}

\hypertarget{sensor-syncronsisation-interface}{%
\section{Sensor syncronsisation
interface}\label{sensor-syncronsisation-interface}}

@@

\begin{itemize}
\tightlist
\item
  Use with \gls{mrp}-library\ref{software-readout-framework}
\item
  Stand-alone mode via sending commands using built-in \gls{cli}
\end{itemize}

@@

@@

\begin{longtable}[]{@{}llll@{}}
\caption{Build sensors with different capabilities
\label{Build_sensors_with_different_capabilities.csv}}\tabularnewline
\toprule
& 1D\ref{d-single-sensor} & 1D: dual sensor & 3D:
Fullsphere\ref{d-fullsphere}\tabularnewline
\midrule
\endfirsthead
\toprule
& 1D\ref{d-single-sensor} & 1D: dual sensor & 3D:
Fullsphere\ref{d-fullsphere}\tabularnewline
\midrule
\endhead
Maximal magnet size & Cubic 30x30x30 & Cubic 30x30x30 & Cubic
20x20x20\tabularnewline
Sensor type & MMC5603NJ & TLV493D & TLV493D\tabularnewline
Sensor count & 1 & 2 & 1\tabularnewline
Scanmode & static (1 point) & static (2 points) & dynamic
(fullsphere)\tabularnewline
\bottomrule
\end{longtable}

@@

As the sensors shown so far relate exclusively to self-built, low-cost
hardware, the following section shows how existing hardware can be
integrated into the system. This is shown here using a
temperature-compensated \passthrough{\lstinline!Voltcraft GM-70!}
telsameter\ref{Voltcraft_GM70_teslameter_with_custom_(+pc)_interface_board.png},
which has a measuring range of \passthrough{\lstinline!0-3T!} with a
resolution of 0.1mT. This offers an \passthrough{\lstinline!RS232!}
interface with a documented
protocol\ref{Voltcraft_GM70_serial_protocol.csv} for connection to a
\gls{pc}. This connectivity makes it possible to make the device
compatible with the \gls{mrp} library using interface software
\cite{VoltcraftGM70Rest} executable on the host \gls{pc}. However,
it does not offer the range of functions that the
\passthrough{\lstinline!Unified Sensor Firmware!}\ref{firmware} offers.

@@

\begin{longtable}[]{@{}lll@{}}
\caption{Voltcraft GM70 serial protocol
\label{Voltcraft_GM70_serial_protocol.csv}}\tabularnewline
\toprule
BYTE-INDEX & REPRESENTATION & VALUE\tabularnewline
\midrule
\endfirsthead
\toprule
BYTE-INDEX & REPRESENTATION & VALUE\tabularnewline
\midrule
\endhead
0 & PREAMBLE & 0x2\tabularnewline
1 & & 0x1\tabularnewline
2 & & 0x4\tabularnewline
3 & UNIT & `B' =\textgreater{} Gauss `E' =\textgreater{}
mT\tabularnewline
5 & POLARITY & `1' =\textgreater{} \emph{0.1 `2' =\textgreater{}
}0.01\tabularnewline
6 & value MSB & 0x-0xFF\tabularnewline
13 & value LSB & 0x-0xFF\tabularnewline
14 & STOP & 0x3\tabularnewline
\bottomrule
\end{longtable}
